---
title: "Federal Elections Exercise"
author: "Alex"
date: "March 08, 2023"
output: github_document
---

# Load, Clean and Join Data 

```{r , message=FALSE, warning=FALSE}
## for data manipulation
library(tidyverse)

## for robust standard errors
library(sandwich)
library(lmtest)

## for printing nice tables
library(stargazer)

## for actually loading data
library(fec16)
```


```{r}
campaigns     <- data.frame(campaigns)
results_house <- data.frame(results_house) %>% 
  filter(party %in% c('DEM', 'REP')) # how many people did we drop? : 
# individuals <- read.csv('./individuals.csv')


```

# Explore and Make Histograms 

```{r make histograms, warning=FALSE}
results_house %>% 
  filter(party %in% c('REP', 'DEM', 'IND')) %>% 
  ggplot() + 
  aes(x=primary_votes, fill=party) + 
  geom_histogram(bins=30, position = 'dodge')
```


# Make a Scatter Plot 

# Run a Regression 

```{r}
model <- lm(primary_votes ~ incumbent + party, data = results_house)
coeftest(model, vcov. = vcovHC)
```

# Print a Table 

```{r}
stargazer(
  model, type = 'text'
)
```


# Interpret the Regression Output 

- We've estimated that a challenger -- i.e. someone who is not currently an incumbent politician, will 
garner `r format(coef(model)['(Intercept)'], digits = 1, big.mark = ',')` votes. 
- We've estimated that an incumbent will get `r format(coef(model)['incumbentTRUE'], digits = 1, big.mark = ',')`
